Experience Report: Distributed Computing for the Common Man

### 2010-03-17 doc/icfp-2010/main.tex
*** empty log message ***

\titlebanner{banner above paper title}        % These are ignored unless
\preprintfooter{short description of paper}   % 'preprint' option specified.

\title{Experience Report: }
\subtitle{Subtitle Text, if any}

@@

>>>>

\titlebanner{submitted to ICFP 2010}        % These are ignored unless
\preprintfooter{Experience Report: Distributed Computing for the Common Man}   % 'preprint' option specified.

\title{Experience Report: Distributed Computing for the Common Man}
%\subtitle{Subtitle Text, if any}

@@

This paper introduces a generic distributed computing library.
It was initially motivated by computing needs that exist in our own
research team. Our applications include large-scale deductive program
verification, which amounts to check the validity of a huge number of
logical formulas using a variety of automated theorem
provers~\cite{filliatre07cav}. Our computing infrastructure consists
of a few powerful multi-core machines (typically 8 to 16 cores) and
several desktop PCs (typically dual-core). However, there is no
library that helps in exploiting such a computing infrastructure in
our favorite functional programming language. Hence we designed and
implemented such a library\footnote{This library is implemented in
  \Ocaml, but the implementation should be straightforward in any
  functional programming language.}, which is the subject of this paper.
